Chemical tagging: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-14 papers/clusters.tex
structure tweaks

% to-do
% - write data and cannon section
% - write method and results section
% - write discussion section
% - put in references
% - cite codes!
% - put in acknowledgement
% - forward to Freeman, others?
% - submit to journal and arXiv

@@

% text shit
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\gaiaeso}{\project{Gaia--\acronym{ESO}}}
\newcommand{\galah}{\project{\acronym{GALAH}}}
\newcommand{\thecannon}{\project{The~Cannon}}
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\eg}{\foreign{e.\,g.}}
\newcommand{\etal}{\foreign{et\,al.}}
\newcommand{\documentname}{\textsl{Article}}

@@

% figure shit
\newcommand{\insanefigure}[1]{%
\includegraphics[width=0.33\textwidth]{./figs/#1_MgFe.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_NaO.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_CN.png}\\
\includegraphics[width=0.33\textwidth]{./figs/#1_AlMg.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_SAl.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_MgK.png}\\
\includegraphics[width=0.33\textwidth]{./figs/#1_HR.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_sky.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_decv.png}}

\begin{document}

@@

\section{Introduction}\label{sec:intro}

@@

\section{Sample and abundances}

MKN: Details about \apogee\ data.

AC: Details about \thecannon\ and implementation.

DWH: Figure showing the full data set; discuss structure.

@@

\clearpage{}
\section{Method and results}

@@

\section{Discussion}

@@

>>>>

% to-do
% - write data and cannon section
% - write method and results section
% - write discussion section
% - put in references
% - cite codes!
% - put in acknowledgement
% - fix all remaining occurrences of ARC, MKN, HWR, or DWH
% - forward to Freeman, others?
% - submit to journal and arXiv

@@

% text shit
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\aspcap}{\project{\acronym{ASPCAP}}}
\newcommand{\gaiaeso}{\project{Gaia--\acronym{ESO}}}
\newcommand{\galah}{\project{\acronym{GALAH}}}
\newcommand{\thecannon}{\project{The~Cannon}}
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\eg}{\foreign{e.\,g.}}
\newcommand{\etal}{\foreign{et\,al.}}
\newcommand{\documentname}{\textsl{Article}}

@@

% figure shit
\newcommand{\insanefigure}[1]{%
\includegraphics[width=0.33\textwidth]{./figs/#1_MgFe.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_NaO.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_CN.png}\\
\includegraphics[width=0.33\textwidth]{./figs/#1_AlMg.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_SAl.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_MgK.png}\\
\includegraphics[width=0.33\textwidth]{./figs/#1_sky.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_decv.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_HR.png}}

\begin{document}\sloppy\sloppypar

@@

\clearpage
\section{Introduction}\label{sec:intro}

@@

\clearpage
\section{Sample and abundances}

The details about how we select, reduce, and analyze the \apogee\ data
are given in full detail in the companion papers \citep{casey16, ness16}.
We summarize briefly here.
For the spectroscopic data, we use the \apogee\ \acronym{DR12}
(\cite{dr12}) spectroscopic data reductions for red-giant stars
($\logg < 3.9$) that are not flagged as bad in the
\apogee\ \aspcap\ (\cite{aspcap}) pipeline reductions.
There are XXXXX stars that make our $\logg$ and flag cuts.

The \apogee\ pipelines deliver stacked (co-added),
pseudo-continuum-normalized spectra, but we do not use these; we
perform our own continuum normalization on individual-exposure data
and co-add it ourselves.
This is required, because the performance of \thecannon\ depends
critically on the methods used for spectral normalization.  It does
not require accurate continuum estimation, but it requires that the
normalization vector be obtained by a \emph{linear operation on the
  data}.
The linear operation we use is a smooth-function fit to pixels
identified as continuum in our previous work \citep{thecannon}.

For the training data labels (used to train \thecannon; see below), we
use the \apogee\ \acronym{DR12} \aspcap\ atmospheric parameters and
15-element abundances, but only for the subset of XXXXX red-giant
stars that have spectral signal-to-noise ratio measurements greater
than 200.
This is a small fraction of the total sample, but these high
signal-to-noise stars are observed to obtain consistent, low-scatter,
sensible abundance-space measurements.

DWH!!  How does \thecannon\ work here?

Six two-dimensional projections of the abundance data, plus some other
data quantities, are shown in \figurename~\ref{fig:all}.

@@

\clearpage
\section{Method and results}

@@

\clearpage
\section{Discussion}

@@

\clearpage
\begin{thebibliography}{24}\raggedright
\bibitem[Ness \etal(2016)]{ness16}
whatev
\end{thebibliography}
